Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-07-06 paper/ms.tex
update manuscript
... minor tweaks

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  Its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  Further observations of
  its stellar obliquity, atmosphere, and mass should confirm its
  planetary nature beyond doubt, and could improve our understanding
  of how the physical and orbital properties of exoplanets change in
  time.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.85\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Spot-induced stellar variability is the dominant signal; flares
    are shown with gray crosses.  Dashed lines indicate the five
    transits observed by TESS.  {\it Bottom}: Zoomed windows of
    individual transits.  Gray lines are the best-fit transit model,
    which includes a local quadratic trend in each window.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements with the local spot-induced variation removed as
    described in Section~\ref{subsec:planet}.  Black points are binned
    to 6-minute intervals, and the error-bar shows the median
    uncertainty for the black points.  The gray line shows the median
    model corresponding to the combined TESS and ground-based transit
    fit (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m; gray points are binned to
    10-minute intervals.  Models show $2\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. A companion dubbed Star A ($\Delta
    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} RV
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
    {\it Top}: for bound companions (EB and HEB scenarios),
		{\it Bottom}: for unassociated companions along the same line of
    sight (BEB scenarios).
		Each constraint is described in Section~\ref{subsec:fp_constraints}.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, $Rp$ Gaia red, and $\omega_{\rm as}$ the parallax in
  arcseconds. 
  \label{fig:hr}
	}
\end{figure}

@@

Reliable ages reported for \cn\ range from 30--46$\,$Myr.  We have
collected ages reported over the years in Table~\ref{tab:ages}.  The
Li depletion boundary technique yields slightly older absolute ages
than isochrone fitting \citep{dobbie_ic_2010,randich_gaiaeso_2018}.
Rather than redetermine the age of the cluster and add another line to
the table, we simply adopt the absolute age range for \tn\ of
30--46$\,$Myr.

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in the open cluster IC 2602.  The
  star and validated planet are therefore between 30 and 46 million
  years old.  The planet is warm ($P = 8.32\,{\rm d}$) and roughly
  Jupiter-sized.  Its transits are grazing: $b > 0.92$ at
  3$\sigma$.  From TESS photometry alone, the planetary size lies
  within 0.68--8.24 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are a cause for concern, as they
  are usually indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  Further observations of
  its stellar obliquity, atmosphere, and mass should confirm its
  planetary nature beyond doubt, and could improve our understanding
  of how the physical and orbital properties of exoplanets change in
  time.
\end{abstract}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.85\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \tn\ from Sectors 10 and 11.} {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares
    are shown with gray crosses.  Dashed lines indicate the five
    transits observed by TESS.  {\it Bottom}: Zoomed windows of
    individual transits.  Gray lines are the best-fit transit model,
    which includes a local quadratic trend in each window.
		\label{fig:rawzoom}
	}
\end{figure*}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements with the local spot-induced variation removed.  Black
    points are binned to 6-minute intervals. The black error-bar shows
    the median uncertainty for the black points.  The gray line is the
    best-fit model to the combined TESS and ground-based data
    (Table~\ref{tab:posterior}).  {\it Bottom:} Multicolor photometry
    from the El Sauce 0.36m; black points are binned to 10-minute
    intervals.  Models show $2\sigma$ lower limits on the transit
    depths in the Cousins-R and Johnson-B bandpasses used to rule out
    specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
    \label{fig:jointphot}
	}
\end{figure*}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Following speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta
    T=4.7$, $2.3''$ west) is detected in the autocorrelation function,
    and is also a resolved Gaia source.  It is co-moving with \tn, and
    its parallax and on-sky position imply that it is physically
    separated from \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:}
    Radial velocity (RV) measurements, with best-fit instrument
    offsets and jitter terms included.  The expected scatter from
    starspots based on $v\sin i$ and the photometric modulation
    amplitude is of order 300m$\,$s$^{-1}$.  {\it Bottom:} RV
    measurements phased to the orbital ephemeris of \pn.  The planet
    is not detected.  The black line shows a circular Keplerian orbit
    representing the $3\sigma$ upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.85\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Astrophysical false positive scenarios.}
    {\it Top}: for bound companions (EB and HEB scenarios),
		{\it Bottom}: for unassociated companions along the same line of
    sight (BEB scenarios).
		Each constraint is described in Section~\ref{subsec:fp_constraints}.
    Gray regions are ruled out by at least one constraint.
		\label{fig:fpscenario}
	}
\end{figure*}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  within 5 standard deviations of the mean \cn\ right ascension,
  declination, and parallax.  $G$ denotes Gaia broadband magnitudes,
  $Bp$ Gaia blue, and $Rp$ Gaia red. 
  \label{fig:hr}
	}
\end{figure}

@@

Reliable ages reported for \cn\ range from 30--46$\,$Myr.  We have
collected ages reported over the years in Table~\ref{tab:ages}.  The
Li depletion boundary technique yields slightly older absolute ages
than isochrone fitting \citep{dobbie_ic_2010,randich_gaiaeso_2018}.
Rather than redetermine the age of the cluster and add another line to
the table, we simply adopt an absolute age range for \tn\ of
30--46$\,$Myr.
